A fast and Low-Overhead Technique to Secure Programs Against Integer Overflows

### 2012-11-15 doc/Manuscript/CGO/paper.tex

%Prunning analysis
\begin{figure}[t!]
\begin{center}
\begin{small}
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}}|l|r|r|r|r|r|}
\hline
Benchmark  &   \#II &  \#E & \%(II, E) &  \#U & \%(II, U) \\ \hline
lbm        &  1,142 &      4 & 99.65\% &      4 & 99.65\% \\ \hline
milc       &  1,573 &  1,070 & 31.98\% &  1,065 & 32.29\% \\ \hline
namd       &  2,965 &  2,900 &  2.19\% &  2,900 &  2.19\% \\ \hline
dealII     & 37,234 & 29,870 & 19.78\% & 28,779 & 22.71\% \\ \hline
soplex     &  3,268 &  2,927 & 10.43\% &  2,897 & 11.35\% \\ \hline
h264ref    & 13,548 & 11,342 & 16.59\% & 11,301 & 16.28\% \\ \hline
astar      &    903 &    808 & 10.52\% &    806 & 10.74\% \\ \hline
sjeng      &  2,483 &  2,354 &  5.20\% &  2,190 & 11.80\% \\ \hline
mcf        &    165 &    164 &  0.61\% &    164 &  0.61\% \\ \hline
omnetpp    &  1,533 &  1,313 & 14.35\% &  1,313 & 14.35\% \\ \hline
gcc        & 16,330 & 15,282 &  6.42\% & 15,110 &  7.47\% \\ \hline
gobmk      & 13,947 & 12,563 &  9.92\% & 12,478 & 10.53\% \\ \hline
libquantum &    943 &    820 & 13.04\% &    817 & 13.36\% \\ \hline
bzip2      &  2,350 &  1,966 & 16.34\% &  1,966 & 16.34\% \\ \hline
hmmer      &  3,963 &  3,346 & 15.57\% &  3,304 & 16.63\% \\ \hline
Total      & 102,347 & 86,688 &        & 85,135 &         \\ \hline
\end{tabular*}
\end{small}
\end{center}
\caption{\label{fig:prunningTable}
Instrumentation library with support of static range analysis.
\#II: number of instructions that have been instrumented without range
analysis.
\#E: number of instructions instrumented in the e-SSA form program.
\#U: number of instructions instrumented in the u-SSA form program.}
\end{figure}

>>>>

%Prunning analysis
\begin{figure}[t!]
\begin{center}
\begin{small}
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}}|l|r|r|r|r|r|}
\hline
Benchmark  &   \#II &  \#E & \%(II, E) &  \#U & \%(II, U) \\ \hline
lbm        &  1,142 &      4 & 99.65\% &      4 & 99.65\% \\ \hline
milc       &  1,602 &  1,070 & 33.21\% &  1,065 & 33.52\% \\ \hline
namd       &  3,234 &  2,900 & 10.33\% &  2,900 & 10.33\% \\ \hline
dealII     & 36,157 & 29,870 & 17.39\% & 28,779 & 20.41\% \\ \hline
soplex     &  3,158 &  2,927 &  7.31\% &  2,897 &  8.26\% \\ \hline
h264ref    & 13,846 & 11,342 & 18.38\% & 11,301 & 18.08\% \\ \hline
astar      &    857 &    808 &  5.72\% &    806 &  5.95\% \\ \hline
sjeng      &  2,504 &  2,354 &  5.99\% &  2,190 & 12.54\% \\ \hline
mcf        &    165 &    164 &  0.61\% &    164 &  0.61\% \\ \hline
omnetpp    &  1,972 &  1,313 & 33.42\% &  1,313 & 33.42\% \\ \hline
gcc        & 18,669 & 15,282 & 18.14\% & 15,110 & 19.06\% \\ \hline
gobmk      & 14,129 & 12,563 & 11.08\% & 12,478 & 11.69\% \\ \hline
libquantum &    928 &    820 & 11.64\% &    817 & 11.96\% \\ \hline
bzip2      &  2,158 &  1,966 &  8.90\% &  1,966 &  8.90\% \\ \hline
hmmer      &  4,001 &  3,346 & 16.37\% &  3,304 & 17.42\% \\ \hline
Total      & 104,522 & 86,688 &        & 85,135 &         \\ \hline
\end{tabular*}
\end{small}
\end{center}
\caption{\label{fig:prunningTable}
Instrumentation library with support of static range analysis.
\#II: number of instructions that have been instrumented without range
analysis.
\#E: number of instructions instrumented in the e-SSA form program.
\#U: number of instructions instrumented in the u-SSA form program.}
\end{figure}
